The Impact of Educational Expenses of New Coders

### 2021-04-15 outputs/paper/paper.Rmd
Edit correlation matrix table

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
```

@@

# Data
```{r, include=FALSE}
#### TODO's ####
# Explain raw data 
#
```

@@

```{r}
#### Descriptive statistics ####
stargazer::stargazer(data.frame(dfNewCoders), type="text")

@@

```{r}
#### Correlation analysis ####

### Print correlation coefficient
round(cor(dfNewCoders), 3)

>>>>

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
library(kableExtra)
```

```{r, include=FALSE}
# Source: https://stefaneng.github.io/apa_correlation_table/
# install.packages("Hmisc")
library(Hmisc)

apply_if <- function(mat, p, f) {
  # Fill NA with FALSE
  p[is.na(p)] <- FALSE
  mat[p] <- f(mat[p])
  mat
}

apaCorr <- function(mat, corrtype = "pearson") {
  matCorr <- mat
  if (class(matCorr) != "rcorr") {
    matCorr <- rcorr(mat, type = corrtype)
  }
  # Add one star for each p < 0.05, 0.01, 0.001
  stars <- apply_if(round(matCorr$r, 2), matCorr$P < 0.05, function(x) paste0(x, "*"))
  stars <- apply_if(stars, matCorr$P < 0.01, function(x) paste0(x, "*"))
  stars <- apply_if(stars, matCorr$P < 0.001, function(x) paste0(x, "*"))
  # Put - on diagonal and blank on upper diagonal
  stars[upper.tri(stars, diag = T)] <- "-"
  stars[upper.tri(stars, diag = F)] <- ""
  n <- length(stars[1,])
  colnames(stars) <- 1:n
  # Remove _ and convert to title case
  row.names(stars) <- tools::toTitleCase(sapply(row.names(stars), gsub, pattern="_", replacement = " "))
  # Add index number to row names
  row.names(stars) <- paste(paste0(1:n,"."), row.names(stars))
  stars
}
```

@@

# Data
```{r, include=FALSE}
#### TODO's ####
# Explain raw data 
# Discuss the variables
#
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Descriptive statistics ####
stargazer::stargazer(data.frame(dfNewCoders), type = "text")

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Correlation analysis ####

### Print correlation coefficient
tblCorr <-
  dfNewCoders %>%
  as.matrix() %>%
  apaCorr() %>%
  data.frame() %>%
  kable(caption = "Correlation matrix for variables",
        booktabs = TRUE,
        col.names = c("1", "2", "3", "4", "5", "6","7","8")) %>%
  footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001",
             general_title = "")

tblCorr
